---
title: "4_chi_topics_success"
output: html_document
---

```{r}

library(ggplot2)
library(corrplot)

```


# Reading data

```{r}

df = read_csv(str_c(sample_path, "corp_new_topics.csv"))

```

# Chi-square

```{r}

df_chi = chisq.test(table(df$state, df$topic))
df_observed = as.data.frame(df_chi$observed)
df_resid = as.data.frame(df_chi$residuals)

# https://www-304.ibm.com/support/docview.wss?uid=swg21..

p6 <-ggplot() +
  geom_tile(data = df_resid, aes(x = Var2, y = Var1, fill = Freq)) +
  geom_text(data = df_observed, aes(x = Var2, y = Var1, label = Freq), size = 3) +
  theme_bw() +
  scale_fill_gradient2(low = "#b2182b",
  mid = "#f7f7f7",
  high = "#2166ac",
  midpoint = 0) +
  theme(axis.text.x = element_text(angle = 90))

p6

ggsave(str_c(path_plots,"states_chisq.png"), 
       plot = p6, device = "png", dpi = 300, width = 15, height = 15)


# topic_titles = c("", "", "", "голосование",
# "строительство", "", "", "")

```

```{r}

df_resid_c = df_resid %>% tidyr::spread(Var2, Freq)
row.names(df_resid_c) = df_resid_c$Var1
df_resid_c$Var1 = NULL
df_resid_c = as.matrix(df_resid_c)

d <- dist(df_resid_c)   # find distance matrix 
hc <- hclust(d)                # apply hirarchical clustering 
plot(hc) 


df_resid$Var1 = factor(df_resid$Var1, levels = rownames(df_resid_c)[hc$order])

```


# Procedure description

1) English stop-words [link:https://github.com/igorbrigadir/stopwords/blob/master/en/snowball_original.txt] were deleted.      
* Additionally, 120 most frequent words were deleted from the text corpus.
2) Texts are only in English


# LDA description

LDA is a probabilistic algorithm, which in practices means that, for instance, two documents (project descriptions) obtain non-zero probabilities to contain or be described by ** all of the Topics **. In order to calculate chi-square for every project description only one Topic having highest probability is chosen. 


```{r}

df_chi = chisq.test(table(df$state, df$topic))
df_observed = as.data.frame(df_chi$observed)
df_resid = as.data.frame(df_chi$residuals)


p6 <- ggplot() +
  geom_tile(data = df_resid, aes(x = Var2, y = Var1, fill = Freq)) +
  geom_text(data = df_observed, aes(x = Var2, y = Var1, label = Freq), size = 3) +
  theme_bw() +
  scale_fill_gradient2("Pearson\nresiduals", 
                       low = "#b2182b", mid = "#f7f7f7", high = "#2166ac", 
                       midpoint = 0, breaks = seq(-5, 25, 5)) +
  theme(axis.text.x = element_text(angle = 90)) + 
  ggtitle(label = "Chi-square test: Topics and Project State",
                  subtitle = str_c("P-Value:", signif(df_chi$p.value, 2))) + 
  xlab("Topic") + ylab("Project's State")
  
p6

ggsave(str_c(path_plots,"states_chisq.png"), 
       plot = p6, device = "png", dpi = 300, width = 15, height = 15)


```


# Chi-square test description

Chi-square test indicates, whether the frequencies of topic-state combinations differ from the expected frequencies (which assumed to be uniform). Pearson residuals indicate the level of a combination frequency exceeds (positive residuals) or fails to reach (negative residuals) expected frequencies. Thus, that rectangles coloured red demonstrate topics, which are less prominent for a given state of the project, while blue colour indicate which topics are typical for a given state. Neuitraly colored are combinations' frequencies, which nearly equals to the expected frequencies, indicating no particular pattern.   

# Figure 1 description

Heretofore, the most strong result is the lack of 9th topic prominence in a description of successful topics. Topics 2 and 3 are not generally typical for the successful projects. Meanwhile, Topic 2 is, as well, does not appears more than expected in projects with a state "failed", which means that it is not reliable to articulate even partial connection between success/failure based on Topic 2.

Meanwhile, Topic 3 provides more confidence for a simplistic connectivity inference. It is appearing more and less than expected in, correspondingly, failed and successful projects. Above-mentioned Topic 9, in it's turn, does not appears far more frequently than expected in projects who failed to gather donations, however, is strongly prominent for projects in a live and canceled states.