---
title: "Untitled"
output: html_document
---

```{r}

library(mongolite)
library(tidyverse)
library(magrittr)
library(lubridate)
library(zoo)
library(gridExtra)

```


```{r}

con <- mongo(db = "kck", url = "mongodb://localhost", collection = "KCK")

```


```{r}

con$iterate()$one()

```

```{r}

con$index()
# con$index(add="id")

```



```{r}

x = 10
over_path = "/home/stlk/Desktop/DigEc_scripts/over_lda/"

df = read_csv(str_c(over_path, "corp_new_topics_",x, ".csv"))


ids = str_c("[", str_c(df$id, collapse = ","), "]")

ids_in = str_c('{"id" : 
               { "$in" : ', ids, ' } }')


# tmp = df$id %>% head(1)
# tmp = str_c("[", str_c(tmp, collapse = ","), "]")
# 
# ids_in = str_c('{"id" :
#                { "$in" : ', tmp, ' } }')


```


```{r}

mongo_path = "/home/stlk/Desktop/DigEc_scripts/mongo_exp/"

# con$count(query = ids_in)

con$find(fields = '{"id" : true, "creator_id" : true, 
         "state_changed_at" : true, 
         "location_country" : true, 
         "category_name" : true, 
         "url_rewards" : true}',
         query = ids_in, pagesize = 100000,
         handler = function(d){
           d <- as.data.frame(d)
           d <- d[,-1]
           d$state_changed_at %<>% as_date()
           d %<>% group_by(id) %>% arrange(desc(state_changed_at)) %>% filter(row_number() == 1)
           write_csv(path = str_c(mongo_path, "_", d$id[1], ".csv"), x = d)
         })

```


# Fixing problem with state_changed_at

```{r}

crt = read_csv("/home/stlk/Desktop/DigEc_scripts/mongo_exp/creators_united.csv")
t = read_csv("/home/stlk/Desktop/DigEc_scripts/mongo_exp/creators_with_time.csv")
t %<>% group_by(id, creator_id) %>% arrange(desc(state_changed_at)) %>% filter(row_number() == 1)

crt = merge(crt %>% dplyr::select(-state_changed_at), t, by = c("id", "creator_id"))
crt$state_changed_at %<>% as_datetime()


```

# Descriptives

```{r}

# crt$creator_id %>% unique() %>% sum()
# dfc$location_country %>% as.factor() %>% summary()
# dfc$category_name %>% as.factor() %>% summary()

# dfc$id %>% as.factor() %>%  unique() %>% length() %>% signif(digits = 15)
# dfc$creator_id %>% as.factor() %>%  unique() %>% length() %>% signif(digits = 15)

```


# Merging creators with main dataset

```{r}

dfc = left_join(df, 
                crt %>% dplyr::select(-group), by = "id")


dfc$state_changed_at %<>% as.character() %>% lubridate::as_datetime()

dfc %<>% group_by(creator_id) %>% arrange(state_changed_at, .by_group = T)

# save(file = "/home/stlk/Desktop/DigEc_scripts/df_with_creators.RData", list = c("dfc"))

```


```{r}

# #!/usr/bin/env Rscript 
# 
# load(file = "/home/stlk/Desktop/DigEc_scripts/df_with_creators.RData")
# 
# dfc$exp = unlist(by(dfc, dfc$creator_id, 
#                     function(x) rank(dfc$state_changed_at, ties.method = "first")))
# 
# save(file = "~/DigEc/df_with_creators.RData", list = c("df_with_creators"))


```

!!# Words used by founders through time !!
!!# Percentage of topics for founders through time !!

# Making experience variable

```{r}

dfc = dfc[!duplicated(dfc$id), ]
crt_ids = dfc$creator_id[duplicated(dfc$creator_id)]

## generate number of row per creator

dfc %<>% group_by(creator_id) %>% mutate(exp = row_number(state_changed_at))

```



# One-time creators


```{r}

dfcp = dfc %>% ungroup() %>% filter(state_new %in% c("successful", "overfunded", "failed"))


dfc_agr = dfcp %>% 
  mutate(month = format(state_changed_at, "%m"), year = format(state_changed_at, "%Y")) %>% 
  group_by(year, month, state_new, topic, add = T) %>% 
  summarise(n_per_topic = n(),
            perc = n_per_topic/nrow(dfcp))

dfc_agr_lag = dfc_agr %>% group_by(year, month, state_new) %>% 
  summarise(n_per_lag = sum(n_per_topic))

dfc_final = left_join(dfc_agr, dfc_agr_lag, by = c("year" , "month", "state_new"))
  

dfc_final = left_join(dfc_final, 
dfc_final %>% group_by(year, month, state_new, topic, add = T) %>% 
  summarise(perc_per_lag = n_per_topic/n_per_lag),
by = c("year", "month", "state_new","topic"))


# Generating Date

dfc_final$date = as.yearmon(dfc_final %$% str_c(year, month, "00", sep = "-"), "%Y-%m") %>% lubridate::as_datetime()



g1 = ggplot(data = dfc_final %>% 
         ungroup() %>% 
         mutate(topic_aggr = ifelse(.$topic %in% c(2,4), "overfunded", 
                                    ifelse(.$topic %in% c(3, 5, 6), "successful", "failed"))) %>% 
         filter(year > 2010)) +
  geom_line(aes(y = perc*100, x = date, group = topic_aggr, colour = as.factor(topic_aggr))) +
  facet_grid(. ~ state_new, scales = "free") + ggtitle("one-time")


g1
```



# Serial creators

```{r}

# choosing creators with exp more than 1

exp_crt_ids = dfc$creator_id[dfc$exp > 1]

plt = dfc %>% filter(creator_id %in% exp_crt_ids)

```



```{r}

## Only successful, overfunded and failed projects are in game 



# calculating proportion of each topic

## check uniqueness of topic per doc

# plt %>% group_by(id, topic) %>% filter(row_number() == 1) # chekced

# plt$state_changed_at %>% head() %>% as.Date(by = "month")

plt %<>% ungroup() %>% filter(state_new %in% c("successful", "overfunded", "failed"))


plt_agr = plt  %>% 
  mutate(month = format(state_changed_at, "%m"), year = format(state_changed_at, "%Y")) %>% 
  group_by(year, month, state_new, topic, add = T) %>% 
  summarise(n_per_topic = n(),
            perc = n_per_topic/nrow(plt))

plt_agr_lag = plt_agr %>% group_by(year, month, state_new) %>% 
  summarise(n_per_lag = sum(n_per_topic))

plt_final = left_join(plt_agr, plt_agr_lag, by = c("year" , "month", "state_new"))
  

plt_final = left_join(plt_final, 
plt_final %>% group_by(year, month, state_new, topic, add = T) %>% 
  summarise(perc_per_lag = n_per_topic/n_per_lag),
by = c("year", "month", "state_new","topic"))


# Generating Date

plt_final$date = as.yearmon(plt_final %$% str_c(year, month, "00", sep = "-"), "%Y-%m") %>% lubridate::as_datetime()

  
```

!!!Compare theese plots with others creators distributions!!!!

```{r}

g2 = ggplot(data = plt_final %>% 
         ungroup() %>% 
         mutate(topic_aggr = ifelse(.$topic %in% c(2,4), "overfunded", 
                                    ifelse(.$topic %in% c(3, 5, 6), "successful", "failed"))) %>% 
         filter(year > 2010)) +
  geom_line(aes(y = perc*100, x = date, group = topic_aggr, colour = as.factor(topic_aggr))) +
  facet_grid(. ~ state_new) + ggtitle("serial")

```



```{r}

grid.arrange(g1, g2, ncol = 1)

p = arrangeGrob(g1, g2, ncol = 1)
ggsave(filename = str_c(path_plots, "enterp_comp.png"), plot = p, device = "png")

```

```{r}

plt$exp_act = ifelse(plt$exp <= q[3], "young", 
                     ifelse(plt$exp %in% (4:8), "experienced", "overexp"))


```

## discritise

```{r}

d_bins = discretize_get_bins(data = plt, input = c("exp"), n_bins = 8)
plt_d = discretize_df(data = plt, data_bins = d_bins, stringsAsFactors=T)

p5 = ggplot(plt, aes(exp)) + geom_bar(fill="#0072B2") + theme_bw() + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

p6=ggplot(plt_d, aes(exp)) + geom_bar(fill="#CC79A7") + theme_bw() + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

grid.arrange(p5,p6,ncol = 2)


```



## Based on experience and state


```{r}

plt_agr = plt %>% 
  mutate(lag = floor_date(state_changed_at, "halfyear")) %>% 
  group_by(lag, topic, state_new, exp_act, add = T) %>% 
  summarise(n_per_topic = n(),
            perc = n_per_topic/nrow(plt))

# consider this to be changed, add exp

plt_agr_lag = plt_agr %>% group_by(lag) %>% 
  summarise(n_per_lag = sum(n_per_topic))

plt_final = left_join(plt_agr, plt_agr_lag, by = c("lag"))
  

plt_final = left_join(plt_final, 
plt_final %>% group_by(lag, topic, state_new, exp_act, add = T) %>% 
  summarise(perc_per_lag = n_per_topic/n_per_lag),
by = c("lag", "topic", "state_new", "exp_act"))


# Generating Date

# plt_final$date = as.yearmon(plt_final %$% str_c(year, month, "00", sep = "-"), "%Y-%m") %>% lubridate::as_datetime()


```


```{r}

ggplot(data = plt_final %>% 
         ungroup() %>% 
         mutate(topic_aggr = ifelse(.$topic %in% c(2,4), "overfunded", 
                                    ifelse(.$topic %in% c(3, 5, 6), "successful", "failed")))) +
  geom_line(aes(y = perc*100, 
                x = lag, 
                color = as.factor(exp_act), 
                group = as.factor(exp_act))) + 
  facet_grid(. ~ as.factor(topic_aggr))




ggplot(data = plt_final %>% 
         ungroup() %>% 
         mutate(topic_aggr = ifelse(.$topic %in% c(2,4), "overfunded", 
                                    ifelse(.$topic %in% c(3, 5, 6), "successful", "failed")))) +
  geom_line(aes(y = perc*100, x = lag, color = as.factor(topic_aggr), group = as.factor(topic_aggr))) + facet_grid(as.factor(exp_act) ~ as.factor(state_new), scales = "free")


ggplot(data = plt_final %>% 
         ungroup() %>% filter(topic %in% c(2,5,10)) %>% 
         mutate(topic_aggr = ifelse(.$topic %in% c(2), "overfunded", 
                                    ifelse(.$topic %in% c(5), "successful", "failed")))) +
  geom_line(aes(y = perc*100, x = lag, color = as.factor(topic_aggr), group = as.factor(topic_aggr))) + facet_grid(as.factor(exp_act) ~ as.factor(state_new), scales = "free")



```



```{r}

dfc %>% ggplot() + geom_bar(aes(x = as.factor(topic)))

```

# x - number of projects, y = topic_percent


```{r}

# aggregating by values

plt_agr = left_join(plt %>%
  group_by(exp, topic) %>% 
  summarise(n_per_topic = n()),
  plt %>%
  group_by(exp) %>% 
  summarise(n_per_exp = n()),
  by = c("exp")) %>% group_by(exp, topic) %>% 
  summarise(perc = n_per_topic/n_per_exp)
  
plt_agr$topic %<>% as.factor()

ggplot(data = plt_agr %>% filter(topic %in% c(2,5,10))) + geom_line(aes(x = exp, y = perc, colour = topic, group = topic))


quantile(dfcp$exp[dfcp$exp > 1], .90)
quantile(dfcp$exp[dfcp$exp > 1])
cut(dfcp$exp[dfcp$exp > 1], breaks = c(2, 3, 6), include.lowest = T, right = T)

```

# aggregating by factors
## topic

```{r}

plt_agr = left_join(plt %>%
  group_by(exp_act, topic) %>% 
  summarise(n_per_topic = n()),
  plt %>%
  group_by(exp_act) %>% 
  summarise(n_per_exp = n()),
  by = c("exp_act")) %>% group_by(exp_act, topic) %>% 
  summarise(perc = n_per_topic/n_per_exp)
  
plt_agr$exp_act %<>% as.factor()
plt_agr$exp_act = factor(plt_agr$exp_act, levels(plt_agr$exp_act)[c(3,1,2)])
plt_agr$topic %<>% as.factor()

ggplot(data = plt_agr) + geom_line(aes(x = exp_act, y = perc, colour = topic, group = topic))

```

## topic_aggr

```{r}

plt_agr = left_join(plt %>% 
                      mutate(topic_aggr = ifelse(.$topic %in% c(2,4), "overfunded", 
                                    ifelse(.$topic %in% c(3, 5, 6), "successful", "failed"))) %>%
  group_by(exp_act, topic_aggr) %>% 
  summarise(n_per_topic = n()),
  plt %>% 
    mutate(topic_aggr = ifelse(.$topic %in% c(2,4), "overfunded", 
                                    ifelse(.$topic %in% c(3, 5, 6), "successful", "failed"))) %>%
  group_by(exp_act) %>% 
  summarise(n_per_exp = n()),
  by = c("exp_act")) %>% group_by(exp_act, topic_aggr) %>% 
  summarise(perc = n_per_topic/n_per_exp)
  
plt_agr$exp_act %<>% as.factor()
plt_agr$exp_act = factor(plt_agr$exp_act, levels(plt_agr$exp_act)[c(3,1,2)])
plt_agr$topic_aggr %<>% as.factor()

ggplot(data = plt_agr) + geom_line(aes(x = exp_act, y = perc, colour = topic_aggr, group = topic_aggr))

```


